A Longitudinal Analysis of the Privacy Paradox

### 2020-05-08 analyses.Rmd
- language updates

```{r}
n_complete <- nrow(d_wide)
age_m <- mean(d_wide$age)
age_sd <- sd(d_wide$age)
male_per <- 1 - mean(d_wide$male)
edu_col_per <- nrow(d_wide[d_wide$edu_num > 5, ]) / n_complete * 100
tibble(
  "N" = n_complete,
  "Age" = age_m,
  "Age SD" = age_sd,
  "Male perc." = male_per,
  "College perc." = edu_col_per
  ) %>% 
  kable() %>% 
  kable_styling("striped")
```

>>>>

```{r}
n_complete <- nrow(d_wide)
age_m <- mean(d_wide$age)
age_sd <- sd(d_wide$age)
male_per <- mean(d_wide$male) - 1
edu_col_per <- nrow(d_wide[d_wide$edu_num > 5, ]) / n_complete * 100
tibble(
  "N" = n_complete,
  "Age" = age_m,
  "Age SD" = age_sd,
  "Male perc." = male_per,
  "College perc." = edu_col_per
  ) %>% 
  kable() %>% 
  kable_styling("striped")
```

### 2020-05-08 analyses_additional.Rmd
- language updates

load("data/workspace.RData") 
```
In what follows, we report the results of additional analyses that were also calculated. For example, for each measure we also report exploratory factor analyses, first order model solutions, and unconstrained solutions to estimate longitudinal  invariance.

@@

```{r include=F}
save.image("data/workspace.RData")
```

>>>>

load("data/workspace.RData") 
```

In what follows, we report the results of additional analyses that were also calculated. For example, for each measure we also report exploratory factor analyses, first order model solutions, and unconstrained solutions to estimate longitudinal  invariance.

@@

```{r include=F, cache=F}
save.image("data/workspace.RData")
```
